Verifying Demonstrations

### 2018-02-27 paper/intro.tex
Changes \ref to \cref

Some of our assumptions (see Section \ref{assumptions} for more
detailed descriptions) are not yet
realized. Not all (or even many) protesters, especially in countries
with oppressive regimes, currently possess smartphones. Digital
certificates signed by a central authority are not yet widely
available and if we rely on government-issued credentials, we cannot prevent the government 
from performing Sybil attacks --- since it can issue arbitrarily many 
\emph{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
demonstrate its \emph{wide 
  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Distance bounding on phones is currently not feasible within a
meaningful range of distance for our scenario.

The assumptions might
become sufficiently realistic in the near future, though, with
smartphone penetration on the rise, increased digitalization and government-issued credentials
available in some countries already now (e.g., Estonia, Germany), and
distance-bounding chips~\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
might not unrealistically be integrated in phones or smartcards in the
future.

>>>>

Some of our assumptions (see \cref{assumptions} for more
detailed descriptions) are not yet
realized. Not all (or even many) protesters, especially in countries
with oppressive regimes, currently possess smartphones. Digital
certificates signed by a central authority are not yet widely
available and if we rely on government-issued credentials, we cannot prevent the government 
from performing Sybil attacks --- since it can issue arbitrarily many 
\emph{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
demonstrate its \emph{wide 
  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
Distance bounding on phones is currently not feasible within a
meaningful range of distance for our scenario.

The assumptions might
become sufficiently realistic in the near future, though, with
smartphone penetration on the rise, increased digitalization and government-issued credentials
available in some countries already now (e.g., Estonia, Germany), and
distance-bounding chips\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
might not unrealistically be integrated in phones or smartcards in the
future, and even phones with off-the-shelf hardware running in
RFID-emulation mode have shown
promising results~\cite{dbonsmartphones}.
